---
title: "p8105_hw6_js5962"
author: "Jiayao Sun"
data: "12/03/2021"
output: html_document
---

```{r setup, echo = FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(mgcv)
library(MASS)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  out.width = "90%",
  message = FALSE,
  warning = FALSE,
  error = FALSE
)

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Import and clean the data

```{r clean}
race = c("White", "Black", "Asian", "Puerto_Rican", "Other", "Unkown") 
birthweight_df = 
  read_csv("birthweight.csv") %>%
  #convert numeric to factor
  mutate(
    babysex = factor(recode(babysex, `1` = "male", `2` = "female")),
    malform = factor(recode(malform, `0` = "absent", `1` = "present")),
    frace = factor(race[frace]),
    mrace = factor(race[mrace])
  ) %>%
  #pnumlbw = 0, pnumsga = 0
  dplyr::select(-pnumlbw, -pnumsga) %>% 
  #check for missing data
  drop_na()
```

To find out a fittest regression model, I would use stepwise regression here, for both forward and backward selection.p value should be smaller than 0.05.

```{r backward}
# fit regression using all predictors
mult_fit = lm(bwt ~ ., data = birthweight_df)
summary(mult_fit)

#use one function
Finalstep = stepAIC(mult_fit, direction = 'both', trace = FALSE, k =  3.8415)
summary(Finalstep)  
```

Therefore, we choose babysexmale, bhead, blength, delwt, gaweeks, mheight, mrace, parity, ppwt and smoken as the significant factors.

Then show a plot of model residuals against fitted values.

```{r residual_fit}
birthweight_df %>% 
  add_predictions(Finalstep) %>% 
  add_residuals(Finalstep) %>% 
  ggplot(aes(x = pred, y = resid, alpha = 0.1)) +
  geom_point(color = "darkblue") +
  ggtitle("residuals against fitted values")
```

Sample

```{r sampling}
birthweight_cv =
  crossv_mc(birthweight_df, 80) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

Next, Fit and compare the models

```{r compare_models}
fit_df =
  birthweight_cv %>% 
  mutate(
    Finalstep = 
      map(.x = train, ~stepAIC(lm(bwt ~ ., data = .x), direction = "both", trace = FALSE)),
    bl_ges = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    bh_bl_sex = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmsefinal = map2_dbl(.x = Finalstep,.y = test, ~rmse(model = .x, data = .y)),
    rmsebl = map2_dbl(.x = bl_ges,.y = test, ~rmse(model = .x, data = .y)),
    rmsebh = map2_dbl(.x = bh_bl_sex,.y = test, ~rmse(model = .x, data = .y))
  )
```

Then we can draw the plot.

```{r violinplot}
fit_df %>% 
  dplyr::select(starts_with("rmse")) %>% 
  pivot_longer(
    rmsefinal:rmsebh,
    names_to = "model",
     values_to = "rmse", 
     names_prefix = "rmse"
   ) %>%
   mutate(
     model = fct_inorder(model)
     ) %>% 
  ggplot(aes(x = model, y = rmse, fill = model, alpha = 0.5)) +
  geom_violin() +
  scale_x_discrete(labels = c("stepwise", "length&gestational", "head&length&sex")) +
  ggtitle("Comparison between three models") +
  scale_fill_discrete(labels = c("stepwise", "length&gestational", "head&length&sex")) +
  ylim(200, 400)
```
